### 2025-06-11 chapters/conclusion/conclusion.tex
counter factual -> counterfactual

Recent advances in machine learning and artificial intelligence (AI) have significantly enhanced researchers' ability to extract information from complex data sets.
Consequently, much of the recent enthusiasm and effort in statistics and computational science over the last decade has been dedicated to expanding the limits, capabilities, and applications of these fields.
While the excitement surrounding machine learning and AI is well-justified, state-space models (SSMs) also play a crucial role in advancing scientific understanding \citep{baker18,hogg24}.
For example, SSMs offer greater interpretability compared to machine learning algorithms, making them valuable for inferring features of dynamic systems.
Moreover, by incorporating real-world mechanisms into their formulations, SSMs have the potential to improve predictions and provide more reliable estimates of the impacts of system interventions.
This latter task is particularly challenging for machine learning algorithms, which depend on existing data, as hypothetical interventions represent counter factual scenarios not present in the data.

>>>>

Recent advances in machine learning and artificial intelligence (AI) have significantly enhanced researchers' ability to extract information from complex data sets.
Consequently, much of the recent enthusiasm and effort in statistics and computational science over the last decade has been dedicated to expanding the limits, capabilities, and applications of these fields.
While the excitement surrounding machine learning and AI is well-justified, state-space models (SSMs) also play a crucial role in advancing scientific understanding \citep{baker18,hogg24}.
For example, SSMs offer greater interpretability compared to machine learning algorithms, making them valuable for inferring features of dynamic systems.
Moreover, by incorporating real-world mechanisms into their formulations, SSMs have the potential to improve predictions and provide more reliable estimates of the impacts of system interventions.
This latter task is particularly challenging for machine learning algorithms, which depend on existing data, as hypothetical interventions represent counterfactual scenarios not present in the data.
